---
title: "r4ds7"
author: "lianrui"
date: "14 December 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data wrangling: 
tibble: variat of df, construction. 
getting data into r: plan-text and others
tidy data: principles, process. 
multiple interelated datasets
regular expression to manipulate strings
categorical data: variable has a fixed set of possible values, nonalphabetical ordering of a string
key tools for dates and date-times. 

# Chapter 7. Tibbles with tibble
```{r}
library(tidyverse)
library(nycflights13)
```


```{r}
# converts existing df to tibble. 
d <- as_tibble(iris); class(d)

# converts tibble to df. 
d <- as.data.frame(d); class(d)
```

```{r}
# create tibbles, tibble()
tibble(x = 1:5, y = 1, z = x^2 + y)

```

Comparing with df: 
1. do not converts strings to factors; 
2. keep raw column names; 
3. allow nonsyntactic names. 
```{r}
tb <- tibble(
        ':)' = 1:5, 
        '...' = 1:5
)
colnames(tb)
```

4. printing: accomodate all columns
```{r}
tibble( 
        a = lubridate:: now() + runif( 1e3) * 86400, 
        b = lubridate:: today() + runif( 1e3) * 30, 
        c = 1: 1e3, d = runif( 1e3), 
        e = sample( letters, 1e3, replace = TRUE)
)

# Wickham, Hadley; Grolemund, Garrett. R for Data Science: Import, Tidy, Transform, Visualize, and Model Data (p. 121). O'Reilly Media. Kindle Edition. 
```

```{r}
# tibble options to show all the columns on the screen. 
options(tibble.width = Inf)
flights %>% View()
```

5. Subsetting. 
```{r}
df <- tibble( x = runif( 5), y = rnorm( 5) )
df[1]; df[,1]

# tibble subsetting with pipe %>%
df %>% .$x

# Wickham, Hadley; Grolemund, Garrett. R for Data Science: Import, Tidy, Transform, Visualize, and Model Data (p. 123). O'Reilly Media. Kindle Edition. 
```

Exercise. 
2. comparing the subsetting behavior of tibble and df. 
```{r}
# df allows partial matching. 
df <- data.frame(abc = 1, xyz = "a")
df$x; df[, "xyz"]; df[,c("abc", "xyz")]
```


```{r}
var <- "mpg"
d <- as_tibble(mtcars)
d[, var]
```

```{r}
?enframe
#Converting atomic vectors to data frames, and vice versa
enframe(1:3)
enframe(c(a = 5, b = 7))
```

