---
title: "r4ds7"
author: "lianrui"
date: "14 December 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data wrangling: 
        tibble: variat of df, construction. 
        getting data into r: plan-text and others
        tidy data: principles, process. 
        multiple interelated datasets
        regular expression to manipulate strings
        categorical data: variable has a fixed set of possible values, nonalphabetical ordering of a string
        key tools for dates and date-times. 

# Chapter 8. Data import with readr
Introduction
Getting started
        compared to base R
Exercises 1
        strings
        factors
        dates, date-times and times
Exercises 2
Parsing a file
        problems
        strategy
        Other strategies
Writing to a file
Other types of data
JSON, xml2: https://jennybc.github.io/purrr-tutorial/.


Introduction
```{r}
library(tidyverse)
```

Getting started
read_csv() 
read_csv2()
read_tsv()
read_delim()
```{r}

```


        compared to base R
Exercises 1
        strings
        factors
        dates, date-times and times
Exercises 2
Parsing a file
        problems
        strategy
        Other strategies
Writing to a file
Other types of data
JSON, xml2: https://jennybc.github.io/purrr-tutorial/.
